### 2020-01-16 defesa/tex/chapter/mcer.tex
wip

	Now suppose that $u$ and $v$ have the $y$-coordinate, that is, the angle between them is $0$. If they are not, a rotation can be applied to make have the same $y$-coordinate. Then, we are going to prove that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that can be used in the proof.

>>>>

	Now suppose that $u$ and $v$ have the same $y$-coordinate, that is, the angle between them is $0$. If they do not, a rotation can be applied to make them have the same $y$-coordinate. Then, the first thing we are proving is that $\Phi_j(u, v) = [0, 2\alpha]$ for a specific case that can be used in the proof.
